\documentclass{report}
\usepackage[utf8]{inputenc}

\title{The Monitoring Box \\ 
Research on how to create an open source data-gathering platform for the Citizen Data Lab
\\ or  \\
Developing an open source, multi-research, geolocation aware, sensor data gathering platform usable by the students and researchers from the Makerslab on the Amsterdam University of Applied Sciences.}

\author{Mick Nieman \\ Amsterdam University of Applied Sciences \and
 Pjotr Scholtze \\ Amsterdam University of Applied Sciences \and
 Heeyeon Joung \\ Amsterdam University of Applied Sciences}
 
\date{January 2017}

\begin{document}

\maketitle

\begin{abstract}
This has no content yet and needs to be filled in.     
\end{abstract}

\tableofcontents

\chapter{Introduction}
This report is written in commision of the Citizen Datalab from Amsterdam. The main goal of this report is to avoid pitfalls and find solutions for making a open source data-gathering platform. 

\section{Statement of Purpose}
This has no content yet and needs to be filled in. 

\section{Statement of Significance}

\chapter{Research Questions}

\section{Overall research question}
What factors contribute to creating an open source, multi-research, sensor geolocation aware, data gathering platform that can be used by the students and researchers from the Makerslab on the Amsterdam University of applied sciences?

\section{Sub-questions}
\begin{enumerate}
\item How technical are the students and researchers from the Makerslab on the Amsterdam University of applied sciences?
\begin{enumerate}
\item What documentation is needed and how detailed should it be
\end{enumerate}
\item What improves the usability of the product when taking the structure plane of user experience into account?
\item How can the data be made available such that the students \& researchers from the Minor Makerslab can use it?
\end{enumerate}

\chapter{Review of literature}

\chapter{Methods}

\chapter{Results}

\chapter{Discussion}

\chapter{Limitations}

\chapter{Conclusion}

\bibliography{Research_Report_Monitoring_Box}


\end{document}
